---
title: "Data"
output:
  html_document: default
  html_notebook: default
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 160)
```
## 1. Legislator Characteristics

### This is a dataset of legislator characteristics that don't change over time. 

You can identify a legislator using "*dni*" (*dni* is unique, *name* may have different versions); you can use "*congre*" (values from 1 to 4 indicating the four congresses included for the last 20 years),"*session*" and "*year*"  to identify time. Columns *session* (integer from 1 to 5) and *year* (name of the congress session, for example: 'C9596') give the same information; there are five **session**s in each **congre**ss. 

```{r, echo=FALSE}
library(jsonlite)
file="https://raw.githubusercontent.com/projectsUW/LegislativeResearchPeru/master/attributes/allAttributes.json?token=AQEW1nx3odgndtaJxXGfviScTlSW3UVrks5ZYVnzwA%3D%3D"
legisDF = fromJSON(file,flatten = F)
##
is.na(legisDF) <- legisDF=="nan"
levs=unique(legisDF$congre)
legisDF$congre=factor(legisDF$congre,levels=levs,ordered = T)
legisDF$period=ifelse(legisDF$congre<'C0102',1,
                      ifelse(legisDF$congre>'C9900' & legisDF$congre<'C0607',2,
                      ifelse(legisDF$congre>'C0506' & legisDF$congre<'C1112',3,4)))

test=legisDF$congre
levels(test)=c(seq(1:5),seq(1:5),seq(1:5),seq(1:5))
legisDF$session=as.numeric(test)

legisDF$party=ifelse(legisDF$party=='ALIANZA ELECTORAL CAMBIO 90 - NUEVA MAYORIA','CAMBIO 90 - NUEVA MAYORIA',legisDF$party)
legisDF$party=ifelse(legisDF$party=='ALIANZA ELECTORAL UNIDAD NACIONAL','UNIDAD NACIONAL',legisDF$party)
legisDF$party=ifelse(legisDF$party=='AGRUPACION INDEPENDIENTE UNION POR EL PERU - SOCIAL DEMOCRACIA','UNION POR EL PERU',legisDF$party)

legisDF$party=ifelse(legisDF$party=='MOVIMIENTO INDEPENDIENTE SOMOS PERU - CAUSA DEMOCRATICA','SOMOS PERU - CAUSA DEMOCRATICA',legisDF$party)

legisDF$party=ifelse(legisDF$party=='FRENTE POPULAR AGRICOLA FIA DEL PERU','FRENTE POPULAR AGRICOLA DEL PERU',legisDF$party)


legisDF$party=ifelse(legisDF$party=='ALIANZA ELECTORAL SOLUCION POPULAR','SOLUCION POPULAR',legisDF$party)

```

```{r,echo=FALSE}
nochange=legisDF[,c(2,5,9,17:22,24,25,28:30)]
nochange=nochange[,c(3,7,13,14,2,9,1,4:6,8,10:12)]
names(nochange)[c(2,3,5,7,14)]=c('name','congre','year','from_capital','reelected_nextElection')
nochange=nochange[order(nochange$dni,nochange$congre,nochange$year),]
row.names(nochange)=NULL
names(nochange)
```
Columns *region* and *from_capital* can not be used in the first Congress (1995-2000), because legilators simply represented the Nation (one district).
Column *experience* counts the previous times a legislator has been in congress; *experience_true* is a boolean version ('1' if previoulsly elected).
Column *governing_true* informs if the legislator belongs to the party in the Executive.
Column *votesPerc* is the share of the preferential votes, from the total preferential votes.

This is how the data set looks (sample):
```{r, echo=FALSE}
head(nochange[,c(1,3,4,10,11,13,14)],20)
```

The column *party* is the name of the party that competed in the elections.

**Download** the time-invariant data set [here](https://github.com/projectsUW/dataSetsScott/blob/master/invariantData.RData?raw=true)

----

### This is a dataset of legislator characteristics that do change over time.

You can identify a legislator using "*dni*"; you can use "*congre*" (values from 1 to 4 indicating the four congresses included for the last 20 years),"*session*" and "*year*"  to identify time. Columns *session* (integer from 1 to 5) and *year* (name of the congress session, for example: 'C9596') give the same information; there are five **session**s in each **congre**ss. 
```{r,echo=FALSE}
change=legisDF[,-c(2,17:22,24,25,28)]
change=change[,c(8,19,20,4,1,3,7,5,6,16,17,18,9:15,2)]
names(change)[c(2,4,8,20)]=c('congre','year','count_proposals','switch_nextYear')
change=change[order(change$dni,change$congre,change$year),]
row.names(change)=NULL
names(change)
```
The column **currentGroup** is the name of the parliamentary group (PG) where the legislator is currently affiliated. **startGroup** informs in what PG the legislator started (it may be different than *party*).
All the variables with the **ei** prefix are measures of homophily, computed from cosponsorship network.

This is how the data set looks (sample):
```{r, echo=FALSE}
head(change[,c(1,2,4,5,9,14,20)],20)
```

**Download** the time-varying data set [here](https://github.com/projectsUW/dataSetsScott/blob/master/varyingData.RData?raw=true)

-----
## 2. Party Characteristics Data

### This is a dataset of parties. 

```{r, echo=FALSE,eval=F}
# library(foreign)
# write.dta(legisDF, "~/Documents/GITHUBs/LegislativeResearchPeru/attributes/legisDFStata.dta")

#legisDF$change=factor(legisDF$change,labels=c('Remained','Switched'))
```

```{r,echo=FALSE}
party=nochange[!duplicated(nochange$dni), ]
party=as.data.frame.matrix(table(party$party,party$congre))
party$name=row.names(party)
row.names(party)=NULL
party=party[,c(5,1:4)]
party$ideology=c(1,1,1,1,1,1,-1,0,-1,0,1,-1,-1,0,0,1,-1,1,0,0,-1,1,1,0,1,-1)
names(party)[c(2:5)]=c('congr_1','congr_2','congr_3','congr_4')
party$inGov_1=0
party$inGov_2=0
party$inGov_3=0
party$inGov_4=0
party[6,7]=1
party[21,8]=1
party[17,9]=1
party[12,10]=1
head(party,20)
```

```{r,echo=FALSE}
invariantData=nochange
save(invariantData,file='invariantData.RData')
varyingData=change
save(varyingData,file='varyingData.RData')
save(party,file='party.RData')
```

**Download** the PARTY data set [here](https://github.com/projectsUW/dataSetsScott/blob/master/party.RData?raw=true)


